---
title: "P8105 Homework 1"
author: "Jia Ji (jj3205)"
date: "2022-09-24"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Problem 1

```{r, echo=FALSE}
library(palmerpenguins)
library(tidyverse)
```

Loading libraries and penguins dataset. 
```{r}
data("penguins", package = "palmerpenguins")
str(penguins)
nrow(penguins)
ncol(penguins)
mean(na.omit(penguins$flipper_length_mm))
```
Dataset penguins includes 344 rows and 8 columns, which are species, islands, bill length, bill depth, flipper length, body mass, sex, and year. The mean flipper length is 200.9152 (mm).

```{r}
length_plot = ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm)) + 
  geom_point(aes(color = species))
ggsave("scatterplot.pdf", length_plot)
```
Export and save the first scatterplot to the project directory.

## Problem 2

```{r}
df = tibble(
  vec_numeric = rnorm(10),
  vec_logical = (vec_numeric > 0),
  vec_char = c("hi", "This", "is", "a", "character", "vector", "of", "length", "ten", "."),
  vec_factor = factor(c("alpha", "beta", "omega", "beta", "beta", "beta", "omega", "alpha",
                        "alpha", "beta"))
)

mean(pull(df,1))
mean(pull(df,2))
mean(pull(df,3))
mean(pull(df,4))



```

The mean of character vector and factor vector cannot work. 

```{r, echo=FALSE}

as.numeric(df$vec_logical)
as.numeric(df$vec_char)
as.numeric(df$vec_factor)

```

We can take the mean of numeric variables and logical variables. Only logical variables and factor variables can be converted to numeric variables. Therefore, we can take the mean of logical variables rather than character variables unless it concludes number.